Probabilistic Catalogs for Crowded Stellar Fields

### 2013-01-18 paper/ms.tex
Number of stars actually within images

The true parameter values for the two simulated data sets are listed in
Table~\ref{tab:truth}. The broken power-law parameter values were chosen so that
roughly half of the stars' fluxes were below and above the break-point
respectively. Figure~\ref{fig:powerlaw} in Appendix~\ref{power_law} also shows the true flux distribution
used for the simulated images. Each of the images
is $100 \times 100$ pixels in extent and covers a range from $-1$ to $1$ in
arbitrary units for both the $x$ and $y$ axes. The first image contains
$\sim$100 stars (including stars just outside of the image) and the second
image contains $\sim$1000 stars. The two simulated images themselves
are shown in Figure~\ref{fig:simulated_data}.

>>>>

The true parameter values for the two simulated data sets are listed in
Table~\ref{tab:truth}. The broken power-law parameter values were chosen so that
roughly half of the stars' fluxes were below and above the break-point
respectively. Figure~\ref{fig:powerlaw} in Appendix~\ref{power_law} also shows the true flux distribution
used for the simulated images. Each of the images
is $100 \times 100$ pixels in extent and covers a range from $-1$ to $1$ in
arbitrary units for both the $x$ and $y$ axes. The first image contains
100 stars (including stars just outside of the image; there are 63 stars actually
centered within the image) and the second
image contains $\sim$1000 stars (699 of which are centered within the image).
The two simulated images themselves
are shown in Figure~\ref{fig:simulated_data}.
